\documentclass[letterpaper,12pt]{article}
%\documentclass[draft,twoside,letterpaper,12pt]{article}

\title{Societal Sadomasochism\footnote{This article is released under Version 3.0 of the ``Attribution (By)'' Creative Commons license and\slash or Version 1.3 of the \textsc{Gnu} Free Documentation License. Originally published online on May 29, 2018. This article-version is hereby published at the Internet Archive on \today , ark:/\discretionary{}{}{}\href{https://archive.org/details/Societal-Sadomasochism}{13960/\dsc t2r59ws9q}.}}

\author{James Redford\footnote{Email address: \textless\href{mailto:jrredford@yahoo.com}{\nolinkurl{jrredford@yahoo.com}}\textgreater .}}

%\date{January 17, 2017}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage[runin]{abstract}
\usepackage{thinsp}
\usepackage[charter]{mathdesign}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{appendix}
\usepackage{attachfile}

\urlstyle{sf}

\renewcommand{\sfdefault}{fvs}

\newcommand{\asterism}{\smash{%
  \raisebox{-.5ex}{%
    \setlength{\tabcolsep}{-.5pt}%
    \begin{tabular}{@{}cc@{}}%
      \multicolumn2c*\\[-2ex]*&*%
    \end{tabular}}}}
\abslabeldelim{\mbox{:\hspace{-0.25em}\quad}}

\newcommand{\dsc}{\discretionary{}{}{}}

\newenvironment{squote}
  {\quote\small}
  {\endquote}
  
\newenvironment{squotation}
  {\quotation\small}
  {\endquotation}
  
\newenvironment{sverse}
  {\verse\small}
  {\endverse}

\frenchspacing
\sloppy
%\fussy
\clubpenalty=5000
\widowpenalty=10000

\begin{document}
\maketitle

\renewcommand{\abstractname}{\textsc{Abstract}}
\setlength{\absparindent}{0.5em}
\begin{abstract}
One cannot understand the extreme schizophrenia and sadomasochistic psychopathy of mankind---and hence the appeal that etatism holds for many---without incorporating the crucial insight provided by psychologist Julian Jaynes in his 1976 monograph \emph{The Origin of Consciousness in the Breakdown of the Bicameral Mind}. And here I'm not speaking of so-called ``aberrant'' human psychology, but rather simply standard human psychology that all humans are born with due to natural evolution.
\end{abstract}

\section{The Problem}
\label{sec:TheProblem}

\emph{The} great age-old social problem that has faced mankind, and still very much does, is that most people do not love themselves, but instead actually hate themselves. Human beings tend to be extreme gluttons for punishment. This can unmistakably be seen in the extreme systems of mass-horror that humans continuously construct for themselves. It's not as if we don't have essentially the entirety of civilizational human history that pointedly warns against such social systems, yet humans are utterly fascinated and enchanted by them, like moths to a flame. Obviously these systems of mass-horror are serving some deep-seated need within the human psyche.

Now, of course, this is not a conscious realization for most people, but rather is a psychological imperative which they are subconsciously controlled by. This has to do with evolutionary psychology, particularly after the Neolithic Revolution and the breakdown of the bicameral mind discussed by psychologist Julian Jaynes in his book \emph{The Origin of Consciousness in the Breakdown of the Bicameral Mind} (Boston: Houghton Mifflin, 1976). It was the widespread belief among the ancients circa three millennia ago and before that they actually directly interacted with the gods. Jaynes's crucial insight was that before the breakdown of the bicameral mind around said era, during the evolution of humans out of an animalistic mental state, that humans were not actually self-conscious, but rather had no choice but to obey the commands of the gods, of which gods were actually one part of the brain communicating with a different part---the sensate, action-response part---via human language that would be heard as actual voices. In other words, our ancestors of circa that era and before were an especially extreme form of schizophrenics.

I haven't heard supporters of Jaynes mention this as an item in Jaynes's favor before, but muscarinic acetylcholine receptor antagonists, such as scopolamine, provide strong evidence for Jaynes's theory---indeed, perhaps the strongest, since it makes the voice-command state Jaynes wrote about completely reproducible. Sociologist Lloyd deMause's work on psychohistory also fits well the Jaynes theory.

Jaynes's theory is also reinforced by Artificial Intelligence researcher Marvin Minsky's concept of the Society of Mind (see Marvin Minsky, illustrations by Juliana Lee, \emph{The Society of Mind} [New York: Touchstone, 1988; 1st ed., 1986]). And both Jaynes and Minsky's ideas on this are restatements and elaborations on Mark 5:1--20 and Luke 8:26--39 involving the Messiah's interaction with a demon-possessed man. When Jesus asked the demon what its name was, the entity replied, ``My name is Legion; for we are many.'' Indeed there are a host of these entities within us all. It's amazing to think that the key to cracking the code of Artificial General Intelligence was given some 2000 years ago within these passages.

The Jaynesian demons can be usefully defined as those subset of Minskian agents which impel people to untowardness, e.g., self-destruction and social destruction.

What a demon is in actuality is a particular type of computer-program operating on the wet-computer of the human brain. Demons are utterly real, but they exist in the exact same ontological manner which the human mind exists, as the human mind is itself a particular type of computer-program operating on the wet-computer of the human brain. The demons are the destructive subsets of the human mind. Science has identified the spiritual realm, and it is the living brain---the living human brain in particular, since that brain is the most complex at present. The spiritual realm exists!

And it's not that these demons actually wish to end life's existence, i.e., that they impel humans toward suicide and societal suicide. Mere nonexistence is not what they seek for us. The actual case of the matter is far, far worse than that. For what these demons actually seek is to send their host and everyone else to Hell for all eternity. The demons are infuriated that they do not have the same level of control they once had over their hosts, when they could issue what was perceived as voice-commands and the host had no choice but to obey---that they are not quite the gods they once were. Via the breakdown of the bicameral mind, the Jaynesian gods of old have more or less been relegated to Tartarus (see 2 Peter 2:4, Young's Literal Translation; Weymouth New Testament; or the note to this passage in the English Standard Version), though they still exercise great control over the subconscious mind and compel humans toward systems of extreme mass-horror.

As I said, these demonic entities are utterly real---as real as any human being, as they ontologically exist in the sameself way as the essence of what a human being is, i.e., the human personality, i.e., the human mind. If one should ever doubt the real existence of these entities, then there are psychological techniques one can use to summon them, such as Astral Projection, as what often follows attempts at Astral Projection is demon-visitation during episodes of sleep paralysis. And one's interaction with these entities can be perceived as being as real as interacting with any other person in external physical reality---nay, sometimes even more real. One can actually have sex with these entities, such as with the succubi and incubi---or what is perceived as such, seemingly every bit as real as sex with any human. Though I only recommend summoning these entities under conditions of actual scientific research, as they are not to be trifled with.

In actuality, what elite occultism is is principally three-pronged: (1) methods of contacting these entities using various mental techniques, including coming into full possession by them; (2) getting people within important social control-sectors to engage in blackmailable behavior so as be able to subjugate them for life; and (3) to provide a spiritual justification for extreme psychopathy. Esoterica at the top echelons is not hokum, but rather utterly practical methods of power. And the demons are outrageous liars who will present themselves as extraterrestrials, departed humans, spirit guides, etc.---though the clandestine scientific psychologists of the deep state, such as with Project \textsc{MKUltra}, undoubtedly know what the actual ontological nature of these entities are.

If most people actually were to love themselves, then essentially all the major social problems of the world would be solved, for then people would not tolerate improper impositions upon themselves; but rather seek freedom for themselves, and thus also for others, for one cannot be free while living in a slave-pit. Yet societies are continuously impelled into various hellpits by subconscious psychological forces whereof most people know not---by the demons lurking within them, whispering into their ear, promising Heaven but delivering Hell. World society is quite literally under demonic control, and the demons have nothing nice in store for anyone, let alone those who make a point of consciously summoning them for power.

\section{Biography of the Author}
\label{sec:BiographyOfTheAuthor}

Born in Austin, Texas and raised in the Leander, Texas hill country, James Redford is a born-again Christian who was converted from atheism by a direct revelation from Jesus Christ. He is a scientific rationalist who concludes that the Omega Point (i.e., the physicists' technical term for God) and the Feynman--DeWitt--Weinberg quantum gravity\slash Standard Model Theory of Everything (\textsc{toe}) is an unavoidable result of the known laws of physics. His website is the following:

\begin{itemize}
\small
\item \emph{Theophysics: God Is the Ultimate Physicist}, ark:/\discretionary{}{}{}\href{https://archive.org/details/Theophysics}{13960/\dsc t3fz13g1p}, \textless\url{https://archive.org/details/Theophysics}\textgreater , \textless\url{http://theophysics.epizy.com}\textgreater , \textless\href{http://theophysics.freevar.com}{\textsf{http\dsc :\dsc //\dsc theophysics\dsc .freevar\dsc .com}}\textgreater .
\end{itemize}

\section{Other Works By the Author}
\label{sec:OtherWorksByTheAuthor}

\begin{itemize}
\small
\item James Redford, ``The Physics of God and the Quantum Gravity Theory of Everything'', \emph{Social Science Research Network} (\emph{SSRN}), Sept. 10, 2012 (orig. pub. Dec. 19, 2011), 186 pp., doi:\discretionary{}{}{}\href{https://dx.doi.org/10.2139/ssrn.1974708}{10\dsc .2139/\dsc ssrn\dsc .1974708}, \textless\href{https://archive.org/download/ThePhysicsOfGodAndTheQuantumGravityTheoryOfEverything/Redford-Physics-of-God.pdf}{\textsf{https\dsc :\dsc //\dsc archive\dsc .org/\dsc download/\dsc The\dsc Physics\dsc Of\dsc God\dsc And\dsc The\dsc Quantum\dsc Gravity\dsc Theory\dsc Of\dsc Everything/\dsc Redford\dsc -Physics\dsc -of\dsc -God\dsc .pdf}}\textgreater , \textless\href{https://purl.org/redford/physics-of-god}{\textsf{https\dsc :\dsc //\dsc purl\dsc .org/\dsc redford/\dsc physics\dsc -of\dsc -god}}\textgreater , \textless\href{https://webcitation.org/74HMsJGbP}{\textsf{https\dsc :\dsc //\dsc webcitation\dsc .org/\dsc 74HMsJGbP}}\textgreater .

\item James Redford, ``Video of Profs. Frank Tipler and Lawrence Krauss's Debate at Caltech: Can Physics Prove God and Christianity?'', \emph{God and Physics Wiki}, May 12, 2019, \textless\href{https://megalodon.jp/2019-0512-1524-14/godandphysics.fandom.com/wiki/Tipler-Krauss_2007_Debate}{\textsf{https\dsc :\dsc //\dsc mega\dsc lodon\dsc .jp/\dsc 2019\dsc -0512\dsc -1524\dsc -14/\dsc god\dsc and\dsc physics\dsc .fandom\dsc .com/\dsc wiki/\dsc Tipler\dsc -Krauss\dsc \_2007\dsc \_Debate}}\textgreater , \textless\href{http://www.freezepage.com/1557642247WROWXLAMHG}{\textsf{http\dsc :\dsc //\dsc www\dsc .freeze\dsc page\dsc .com/\dsc 1557642247\dsc WROWXLAMHG}}\textgreater , \textless\href{https://web.archive.org/web/20190512065553/http://theophysics.freevar.com/Tipler-Krauss_2007_Debate.html}{\textsf{https\dsc :\dsc //\dsc web\dsc .archive\dsc .org/\dsc web/\dsc 20190512\dsc 065553/\dsc http\dsc :\dsc //\dsc theo\dsc physics\dsc .freevar\dsc .com/\dsc Tipler\dsc -Krauss\dsc \_2007\dsc \_Debate\dsc .html}}\textgreater , \textless\href{https://archive.is/V9njw}{\textsf{https\dsc :\dsc //\dsc archive\dsc .is/\dsc V9njw}}\textgreater .

\item James Redford, ``Jesus Is an Anarchist'', \emph{Social Science Research Network} (\emph{SSRN}), Dec.~4, 2011 (orig. pub. Dec. 19, 2001), 60 pp., doi:\discretionary{}{}{}\href{https://dx.doi.org/10.2139/ssrn.1337761}{10\dsc .2139/\dsc ssrn\dsc .1337761}, \textless\href{https://archive.org/download/JesusIsAnAnarchist/Redford-Jesus-Is-an-Anarchist.pdf}{\textsf{https\dsc :\dsc //\dsc archive\dsc .org/\dsc download/\dsc Jesus\dsc Is\dsc An\dsc Anarchist/\dsc Redford\dsc -Jesus\dsc -Is\dsc -an\dsc -Anarchist\dsc .pdf}}\textgreater , \textless\href{https://web.archive.org/web/20120425000701/http://theophysics.host56.com/anarchist-jesus.pdf}{\textsf{https\dsc :\dsc //\dsc web\dsc .archive\dsc .org/\dsc web/\dsc 20120425000701/\dsc http\dsc :\dsc //\dsc theophysics\dsc .host56\dsc .com/\dsc anarchist\dsc -jesus\dsc .pdf}}\textgreater , \textless\href{https://webcitation.org/66AF4TMv3}{\textsf{https\dsc :\dsc //\dsc webcitation\dsc .org/\dsc 66AF4TMv3}}\textgreater .

\item James Redford, ``Libertarian Anarchism Is Apodictically Correct'', \emph{Social Science Research Network} (\emph{SSRN}), Dec. 15, 2011, 9~pp., doi:\discretionary{}{}{}\href{https://dx.doi.org/10.2139/ssrn.1972733}{10\dsc .2139/\dsc ssrn\dsc .1972733}, \textless\href{https://archive.org/download/LibertarianAnarchismIsApodicticallyCorrect/Redford-Apodictic-Libertarianism.pdf}{\textsf{https\dsc :\dsc //\dsc archive\dsc .org/\dsc download/\dsc Libertarian\dsc Anarchism\dsc Is\dsc Apodictically\dsc Correct/\dsc Redford\dsc -Apodictic\dsc -Libertarianism\dsc .pdf}}\textgreater , \textless\href{https://web.archive.org/web/20120831123938/http://theophysics.host56.com/Redford-Apodictic-Libertarianism.pdf}{\textsf{https\dsc :\dsc //\dsc web\dsc .archive\dsc .org/\dsc web/\dsc 20120831\dsc 123938/\dsc http\dsc :\dsc //\dsc theophysics\dsc .host56\dsc .com/\dsc Redford\dsc -Apodictic\dsc -Libertarianism\dsc .pdf}}\textgreater , \textless\href{https://webcitation.org/69H4tzCOZ}{\textsf{https\dsc :\dsc //\dsc webcitation\dsc .org/\dsc 69H4tzCOZ}}\textgreater .
\end{itemize}

\end{document}
